Probing the Deuteron at Very Large Internal Momenta

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/authorlist.tex
updated article submission docs

%Author List from Spring 2018 Hall C Commissioning + SIDIS Runs
%Comment / Uncomment accordingly
\author{C.~Yero$^{1,15}$}       %Main author for E12-10-003 experiment
\homepage[ORCiD: ]{https://orcid.org/0000-0003-2822-7373}
\email[email: ]{cyero@jlab.org}
%\email[email: ]{cyero@jlab.org}
\author{D.~Abrams$^{2}$}           %Commissioning ONLY
\author{Z.~Ahmed$^{3}$}            %Commissioning ONLY
\author{A.~Ahmidouch$^{4}$}        % . . .----> HOLLY
\author{B.~Aljawrneh$^{4}$}        %Commissioning ONLY
\author{S.~Alsalmi$^{5}$}          %Commissioning ONLY
\author{R.~Ambrose$^{3}$}          %Commissioning + SIDIS
%\author{D.~Androic}         %Color Transparency ONLY
\author{W.~Armstrong$^{6}$}        %Commissioning ONLY
\author{A.~Asaturyan$^{7}$}        %Commissioning ONLY
\author{K.~Assumin-Gyimah$^{8}$}   %Commissioning ONLY
\author{C.~Ayerbe Gayoso$^{9}$}    %Commissioning + SIDIS
\author{A.~Bandari$^{9}$}          %Commissioning + SIDIS
\author{J.~Bane$^{10}$}             %Deuteron Experiment ONLY
\author{S.~Basnet$^{3}$}           %Commissioning + SIDIS
\author{V.V.~Berdnikov$^{11}$}        %Commissioning + SIDIS  (tell HOLLY name change)
\author{J.~Bericic$^{15}$}          %SHMS Optics Contributor  HOLLY
\author{H.~Bhatt$^{8}$}            %Commissioning + SIDIS
\author{D.~Bhetuwal$^{8}$}         %Commissioning + SIDIS
\author{D.~Biswas$^{12}$}           %Commissioning + SIDIS
\author{W.U.~Boeglin$^{1}$}          %Commissioning ONLY (Deuteron Spokesperson)
\author{P.~Bosted$^{9}$}           %Commissioning ONLY (SIDIS Spokesperson)
\author{E.~Brash$^{13}$}            %Commissioning ONLY
\author{M.H.S.~Bukhari$^{14}$}          %Commissioning ONLY
%\author{M.~Carmignotto}     %NO MINIMUM SHIFTS
\author{H.~Chen$^{2}$}             %Commissioning ONLY
\author{J.P.~Chen$^{15}$}           %Commissioning ONLY
\author{M.~Chen$^{2}$}             %Commissioning ONLY
\author{M.E.~Christy$^{12}$}          %Commissioning ONLY
\author{S.~Covrig$^{15}$}           %Commissioning + SIDIS               
\author{K.~Craycraft$^{10}$}        %Commissioning + SIDIS
\author{S.~Danagoulian$^{4}$}            %NO MINIMUM SHIFTS. Contributed to detectros
\author{D.~Day$^{2}$}             %ONLY DEC. 2017 Spec. Commissioning Contributed to Noble Gas Detector
\author{M.~Diefenthaler$^{15}$}     %Commissioning + SIDIS
\author{M.~Dlamini$^{17}$}          %Commissioning ONLY
\author{J.~Dunne$^{8}$}
%Commissioning ONLY
\author{B.~Duran$^{16}$}            %Commissioning + SIDIS
\author{D.~Dutta$^{8}$}            %Commissioning + SIDIS  (CT Spokesperson)
\author{R.~Ent$^{15}$}              %NO MINIMUM SHIFTS JLab Physics Division Leader (SIDIS Co-Spokesperson) (should be included)??????
\author{R.~Evans$^{3}$}            %Commissioning ONLY
\author{H.~Fenker$^{15}$}           %Commissioning + SIDIS
%\author{I.~Fernando}        %NO MINIMUM SHIFTS
\author{N.~Fomin$^{10}$}            %Commissioning ONLY
\author{E.~Fuchey$^{18}$}           %Commissioning ONLY
\author{D.~Gaskell$^{15}$}          %Commissioning + SIDIS
\author{T.N.~Gautam$^{12}$}         %Commissioning ONLY
\author{F.A.~Gonzalez$^{19}$}       %Commissioning + SIDIS
\author{J.O.~Hansen$^{15}$}           %Commissioning ONLY
\author{F.~Hauenstein$^{20}$}       %Commissioning ONLY
\author{A.V.~Hernandez$^{11}$}       %Commissioning ONLY
\author{T.~Horn$^{11}$}             %Commissioning ONLY
\author{G.M.~Huber$^{3}$}            %Commissioning ONLY
\homepage[ORCiD: ]{http://orcid.org/0000-0002-5658-1065}
\author{M.K.~Jones$^{15}$}          %Commissioning + SIDIS
\author{S.~Joosten$^{6}$}          %Commissioning ONLY
\author{M.L.~Kabir$^{8}$}          %Commissioning + SIDIS           
%\author{N.~Kalantarians}    %NO MINIMUM SHIFTS
\author{A.~Karki$^{8}$}            %Commissioning + SIDIS  
\author{C.E.~Keppel$^{15}$}           %NO MINIMUM SHIFTS Hall A/C Leader (F2 Spokesperson) 
\author{A.~Khanal$^{1}$}           %Commissioning ONLY
\author{P.~King$^{17}$}             %Commissioning ONLY
\author{E.~Kinney$^{21}$}           %Commissioning ONLY (SIDIS Co-Spokesperson)
%\author{H.S.~Ko}            %Color Transparency ONLY
%\author{M.~Khol}            %NO MINIMUM SHIFTS
\author{N.~Lashley-Colthirst$^{12}$}      %Commissioning ONLY
\author{S.~Li$^{22}$}               %Commissioning ONLY
\author{W.B.~Li$^{9}$}               %Commissioning ONLY  tell HOLLY name change
\author{A.H.~Liyanage$^{12}$}       %Commissioning + SIDIS
\author{D.J.~Mack$^{15}$}             %Commissioning + SIDIS
\author{S.P.~Malace$^{15}$}           %Commissioning + SIDIS (F2 Spokesperson)
%\author{P.~Markowitz}       %NO MINIMUM SHIFTS
\author{J.~Matter$^{2}$}           %Commissioning + SIDIS
\author{D.~Meekins$^{15}$}          %NO MINIMUM SHIFTS (TARGET WORK DURING COMMISSIONING+SIDIS. (INCLUDED AS AUTHOR!)
\author{R.~Michaels$^{15}$}         %Commissioning + SIDIS
\author{A.~Mkrtchyan$^{7}$}        %Commissioning ONLY     HOLLY
\author{H.~Mkrtchyan$^{7}$}        %Commissioning ONLY
\author{S.J.~Nazeer$^{12}$}         %Commissioning ONLY
\author{S.~Nanda$^{8}$}           %Spec. commissioning only Dec. 14-17 shifts
\author{G.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
\author{M.~Niculescu$^{23}$}        %Took 11 shifts (Why is NOT included in Holly's list) ??????
\author{D.~Nguyen$^{2}$}           %Commissioning ONLY (Took 10 shifts) 
\author{N.~Nuruzzaman$^{24}$}       %Commissioning ONLY
\author{B.~Pandey$^{12}$}           %NO MINIMUM SHIFTS (WORKED ON HMS DCs for 1 year. INCLUDED AS AUTHOR!)
\author{S.~Park$^{19}$}             %Commissioning + SIDIS
\author{C.F.~Perdrisat$^{9}$}            %College of William & Mary   HOLLY
\author{E.~Pooser$^{15}$}           %Commissioning + SIDIS
%\author{A.~Puckett}         %NO MINIMUM SHIFTS
\author{M.~Rehfuss$^{16}$}          %Commissioning ONLY
\author{J.~Reinhold$^{1}$}         %Commissioning ONLY
%\author{N.~Santiesteban}     %Color Transparency ONLY
\author{B.~Sawatzky$^{15}$}          %Color Transparency ONLY (Worked on DAQ/Detector. INCLUDED AS AUTHOR!)
\author{G.R.~Smith$^{15}$}             %Commissioning ONLY
\author{A.~Sun$^{25}$}               %Commissioning + SIDIS
\author{H.~Szumila-Vance$^{15}$}     %Commissioning + SIDIS
%\author{A.~Tadepalli}        %F2 ONLY
\author{V.~Tadevosyan$^{7}$}        %Commissioning + SIDIS
%\author{R.~Trotta}           %NO MINIMUM SHIFTS
\author{S.A.~Wood$^{15}$}            %NO MINIMUM SHIFTS (Hall C Deputy + Worked on Hall C 12 GeV software + hardware work) (INCLUDED AS AUTHOR!)
\author{J.~Zhang$^{19}$}        %Commissioning ONLY 
%\author{Jixie~Zhang}          %NO MINIMUM SHIFTS
\collaboration{for the Hall C Collaboration}
\affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
\affiliation{$^{2}$University of Virginia, Charlottesville, Virginia 22903, USA}
\affiliation{$^{3}$University of Regina, Regina, Saskatchewan S4S 0A2, Canada}
\affiliation{$^{4}$North Carolina Agricultural and Technical State University, Greensboro, North Carolina 27411, USA}
\affiliation{$^{5}$Kent State University, Kent, Ohio 44240, USA}
\affiliation{$^{6}$Argonne National Laboratory, Lemont, Illinois 60439, USA}   %fixed address for Whit and Sylvester
\affiliation{$^{7}$A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute), 2 Alikhanian Brothers Street, 0036, Yerevan, Armenia}
\affiliation{$^{8}$Mississippi State University, Mississippi State, Mississippi 39762, USA}
\affiliation{$^{9}$The College of William \& Mary, Williamsburg, Virginia 23185, USA}
\affiliation{$^{10}$University of Tennessee, Knoxville, Tennessee 37996, USA}
\affiliation{$^{11}$Catholic University of America, Washington, DC 20064, USA}
\affiliation{$^{12}$Hampton University, Hampton, Virginia 23669, USA}
\affiliation{$^{13}$Christopher Newport University, Newport News, Virginia 23606, USA}
\affiliation{$^{14}$Jazan University, Jazan 45142, Saudi Arabia}
\affiliation{$^{15}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
\affiliation{$^{16}$Temple University, Philadelphia, Pennsylvania 19122, USA}
\affiliation{$^{17}$Ohio University, Athens, Ohio 45701, USA}
\affiliation{$^{18}$University of Connecticut, Storrs, Connecticut 06269, USA}
\affiliation{$^{19}$Stony Brook University, Stony Brook, New York 11794, USA}
\affiliation{$^{20}$Old Dominion University, Norfolk, Virginia 23529, USA}
\affiliation{$^{21}$University of Colorado Boulder, Boulder, Colorado 80309, USA}
\affiliation{$^{22}$University of New Hampshire, Durham, New Hampshire 03824, USA}
\affiliation{$^{23}$James Madison University, Harrisonburg, Virginia 22807, USA}
\affiliation{$^{24}$Rutgers University, New Brunswick, New Jersey 08854, USA}
\affiliation{$^{25}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}

>>>>

%Author List from Spring 2018 Hall C Commissioning + SIDIS Runs
\author{C.~Yero$^{1,15}$}       %Main author for E12-10-003 experiment
\homepage[ORCiD: ]{https://orcid.org/0000-0003-2822-7373}
\email[email: ]{cyero@jlab.org}
\author{D.~Abrams$^{2}$}           
\author{Z.~Ahmed$^{3}$}            
\author{A.~Ahmidouch$^{4}$}        
\author{B.~Aljawrneh$^{4}$}        
\author{S.~Alsalmi$^{5}$}          
\author{R.~Ambrose$^{3}$}          
\author{W.~Armstrong$^{6}$}        
\author{A.~Asaturyan$^{7}$}        
\author{K.~Assumin-Gyimah$^{8}$}   
\author{C.~Ayerbe Gayoso$^{9}$}    
\author{A.~Bandari$^{9}$}          
\author{J.~Bane$^{10}$}            
\author{S.~Basnet$^{3}$}           
\author{V.V.~Berdnikov$^{11}$}     
\author{J.~Bericic$^{15}$}         
\author{H.~Bhatt$^{8}$}            
\author{D.~Bhetuwal$^{8}$}         
\author{D.~Biswas$^{12}$}          
\author{W.U.~Boeglin$^{1}$}        
\author{P.~Bosted$^{9}$}           
\author{E.~Brash$^{13}$}           
\author{M.H.S.~Bukhari$^{14}$}     
\author{H.~Chen$^{2}$}             
\author{J.P.~Chen$^{15}$}          
\author{M.~Chen$^{2}$}             
\author{M.E.~Christy$^{12}$}       
\author{S.~Covrig$^{15}$}          
\author{K.~Craycraft$^{10}$}       
\author{S.~Danagoulian$^{4}$}      
\author{D.~Day$^{2}$}             
\author{M.~Diefenthaler$^{15}$}    
\author{M.~Dlamini$^{17}$}         
\author{J.~Dunne$^{8}$}
\author{B.~Duran$^{16}$}          
\author{D.~Dutta$^{8}$}          
\author{R.~Ent$^{15}$}            
\author{R.~Evans$^{3}$}           
\author{H.~Fenker$^{15}$}         
\author{N.~Fomin$^{10}$}          
\author{E.~Fuchey$^{18}$}         
\author{D.~Gaskell$^{15}$}        
\author{T.N.~Gautam$^{12}$}       
\author{F.A.~Gonzalez$^{19}$}     
\author{J.O.~Hansen$^{15}$}       
\author{F.~Hauenstein$^{20}$}     
\author{A.V.~Hernandez$^{11}$}    
\author{T.~Horn$^{11}$}           
\author{G.M.~Huber$^{3}$}         
\homepage[ORCiD: ]{http://orcid.org/0000-0002-5658-1065}
\author{M.K.~Jones$^{15}$}         
\author{S.~Joosten$^{6}$}          
\author{M.L.~Kabir$^{8}$}            
\author{A.~Karki$^{8}$}           
\author{C.E.~Keppel$^{15}$}          
\author{A.~Khanal$^{1}$}       
\author{P.~King$^{17}$}             
\author{E.~Kinney$^{21}$}           
\author{N.~Lashley-Colthirst$^{12}$}     
\author{S.~Li$^{22}$}               
\author{W.B.~Li$^{9}$}              
\author{A.H.~Liyanage$^{12}$}       
\author{D.J.~Mack$^{15}$}           
\author{S.P.~Malace$^{15}$}         
\author{J.~Matter$^{2}$}           
\author{D.~Meekins$^{15}$}          
\author{R.~Michaels$^{15}$}         
\author{A.~Mkrtchyan$^{7}$}        
\author{H.~Mkrtchyan$^{7}$}        
\author{S.J.~Nazeer$^{12}$}         
\author{S.~Nanda$^{8}$}           
\author{G.~Niculescu$^{23}$}        
\author{M.~Niculescu$^{23}$}        
\author{D.~Nguyen$^{2}$}           
\author{N.~Nuruzzaman$^{24}$}       
\author{B.~Pandey$^{12}$}           
\author{S.~Park$^{19}$}             
\author{C.F.~Perdrisat$^{9}$}       
\author{E.~Pooser$^{15}$}           
\author{M.~Rehfuss$^{16}$}          
\author{J.~Reinhold$^{1}$}         
\author{B.~Sawatzky$^{15}$}         
\author{G.R.~Smith$^{15}$}          
\author{A.~Sun$^{25}$}              
\author{H.~Szumila-Vance$^{15}$}    
\author{V.~Tadevosyan$^{7}$}        
\author{S.A.~Wood$^{15}$}           
\author{J.~Zhang$^{19}$}

\collaboration{for the Hall C Collaboration}
\affiliation{$^{1}$Florida International University, University Park, Florida 33199, USA}
\affiliation{$^{2}$University of Virginia, Charlottesville, Virginia 22903, USA}
\affiliation{$^{3}$University of Regina, Regina, Saskatchewan S4S 0A2, Canada}
\affiliation{$^{4}$North Carolina Agricultural and Technical State University, Greensboro, North Carolina 27411, USA}
\affiliation{$^{5}$Kent State University, Kent, Ohio 44240, USA}
\affiliation{$^{6}$Argonne National Laboratory, Lemont, Illinois 60439, USA}  
\affiliation{$^{7}$A.I. Alikhanyan National Science Laboratory (Yerevan Physics Institute), 2 Alikhanian Brothers Street, 0036, Yerevan, Armenia}
\affiliation{$^{8}$Mississippi State University, Mississippi State, Mississippi 39762, USA}
\affiliation{$^{9}$The College of William \& Mary, Williamsburg, Virginia 23185, USA}
\affiliation{$^{10}$University of Tennessee, Knoxville, Tennessee 37996, USA}
\affiliation{$^{11}$Catholic University of America, Washington, DC 20064, USA}
\affiliation{$^{12}$Hampton University, Hampton, Virginia 23669, USA}
\affiliation{$^{13}$Christopher Newport University, Newport News, Virginia 23606, USA}
\affiliation{$^{14}$Jazan University, Jazan 45142, Saudi Arabia}
\affiliation{$^{15}$Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
\affiliation{$^{16}$Temple University, Philadelphia, Pennsylvania 19122, USA}
\affiliation{$^{17}$Ohio University, Athens, Ohio 45701, USA}
\affiliation{$^{18}$University of Connecticut, Storrs, Connecticut 06269, USA}
\affiliation{$^{19}$Stony Brook University, Stony Brook, New York 11794, USA}
\affiliation{$^{20}$Old Dominion University, Norfolk, Virginia 23529, USA}
\affiliation{$^{21}$University of Colorado Boulder, Boulder, Colorado 80309, USA}
\affiliation{$^{22}$University of New Hampshire, Durham, New Hampshire 03824, USA}
\affiliation{$^{23}$James Madison University, Harrisonburg, Virginia 22807, USA}
\affiliation{$^{24}$Rutgers University, New Brunswick, New Jersey 08854, USA}
\affiliation{$^{25}$Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}

### 2020-08-18 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/cover_letter/cl.tex
updated article submission docs

\begin{document}
\begin{letter}{Carlos Yero\\
Thomas Jefferson National Accelerator Facility\\
12000 Jefferson Avenue \\
Newport News, VA 23602\\
(786) 387-8667 \\
cyero@jlab.org
  }

\opening{Dear Editors,\\}

I hereby submit a manuscript entitled ``Probing the Deuteron at Very Large Internal Momenta'' to be considered
for publication by \textit{Physical Review Letters}. There are eight files in all: the main manuscript file (prl.tex), 2 figure files (.pdf),
a biblipgraphy file (.bbl), an author list file (.tex), and three supplementary (.txt) files with the numerical results of the
cross sections evaluated at the relevant kinematics described in the manuscript.\\

We report cross-section measurements of the $^{2}$H$(e,e'p)n$ at neutron recoil momenta up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c which is almost
double the maximum recoil momentum measured in a previous deuteron electro-disintegration experiment carried out in Hall A at Jefferson Lab. 
That experiment concluded that at neutron recoil angles $35^{\circ}\leq \theta_{nq}\leq 45^{\circ}$, final state interactions (FSI) are largely
reduced and the plane wave impulse approximation (PWIA) provided the dominant contribution to the cross section. This experiment focused
on the kinematic window (where FSI are small) found by the Hall A experiment and extended the missing momentum coverage from $p_{\mathrm{r}}\sim0.5 - 1.0$ GeV/c, giving
access to the high momentum component of the deuteron wave-function, or equivalently, the nucleon-nucleon ($NN$) interaction at the sub-Fermi
distance scale which is currently poorly understood.\\

This Letter summarizes the experimental results of cross-section measurements that extended the neutron recoil momentum measured up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c giving a direct access
to the shot-range structure of the deuteron wave-function which is a crucial step forward in the understanding the $NN$ interaction at very small ($\leq$1 fm) distances. We believe these
findings will be of general interest to the readers of your journal.\\

We declare that this manuscript is original, has not been published before and is not currently being considered for publication elsewhere.\\
\\
\closing{Sincerely,
%\includegraphics[width=6cm]{signature.pdf}
}
%I made a pdf file of my signature using the scanner, so that all the cover letters I sent
%electronically were "signed."

Carlos Yero\\
Hall C Postdoctoral Fellow\\
\end{letter}

>>>>

\begin{document}
\begin{letter}{
    Dr. Michael Thoennessen\\
    Editor-in-Chief, APS Editorial Office \\
    \textit{Physical Review Letters} (PRL)\\
    }

\opening{Dear Dr. Thoennessen,\\}

I hereby submit a manuscript entitled ``Probing the Deuteron at Very Large Internal Momenta'' to be considered for publication by \textit{Physical Review Letters}.
There are eight files in all: the main manuscript file (ms.tex), 2 figure files (.pdf), a bibliography file (.bbl), an author list file (.tex), and three supplementary (.txt)
files with the numerical results of the cross sections evaluated at the relevant kinematics described in the manuscript.\\

We report cross section measurements of the $^{2}$H$(e,e'p)n$ at neutron recoil momenta up to $p_{\mathrm{r}}\sim$ 1.0 GeV/c which is almost
double the maximum recoil momentum measured in a previous deuteron electro-disintegration experiment carried out in Hall A at Jefferson Lab. 
The Hall A experiment concluded that at neutron recoil angles $35^{\circ}\leq \theta_{nq}\leq 45^{\circ}$, final state interactions (FSI) are largely
reduced and the plane wave impulse approximation (PWIA) provides the dominant contribution to the cross section. This experiment focuses
on the kinematic window (where FSI are small) previously found in Hall A and extends the missing momentum coverage from $p_{\mathrm{r}}\sim0.5 - 1.0$ GeV/c, giving
direct access to the high momentum component of the deuteron wave-function. This is a crucial step forward in the understanding the nucleon-nucleon ($NN$) interaction at
the sub-Fermi distance scale which is currently poorly understood. We believe these findings will be of general interest to the readers of your journal.\\

We declare that this manuscript is original, has not been published before in a peer-reviewed journal and is not currently being considered for publication elsewhere.\\
\\
\closing{Sincerely,
%\includegraphics[width=6cm]{signature.pdf}
}
%I made a pdf file of my signature using the scanner, so that all the cover letters I sent
%electronically were "signed."  
Carlos Yero\\
Hall C Postdoctoral Research Fellow\\
Thomas Jefferson National Accelerator Facility\\
12000 Jefferson Avenue \\
Newport News, VA 23602\\
e-mail: cyero@jlab.org\\
phone: (786) 387-8667

\end{letter}
